---
title: "CA HR2W - Violations"
author: "Team: Below The Mean"
date: "5/19/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(janitor)
library(urbnmapr)
```

### Human Right to Water (HR2W)

Every human being has the right to safe, clean, affordable, and accessible water adequate for human consumption, cooking, and sanitary purposes.

We’ve decided to focus our efforts on examining active violations of the HR2W dataset. The dataset contains ~6,400 violations with interesting characteristics about violation type, analyte in violation, amount above threshold, as well as date and time of violation.

We want to answer questions such as:

1. Where are the most violations occurring over time?
2. What are the most common violations?
3. What is the response time to resolution of violations? Do more affluent counties have quicker resolution times?
4. What analytes show the largest departure from acceptable threshold on average?



```{r}
ca_counties <- urbnmapr::counties %>% 
  filter(state_abbv == "CA") %>% 
  clean_names() %>% 
  mutate(county_name = tolower(str_replace(county_name, " County", "")))

act_vio <- read_csv("data/04_water-regulatory-information/hr2w_web_data_active_2-2019.csv") %>% 
  clean_names() %>% 
  mutate(county = tolower(county)) %>% 
  separate(col = result, into = c("result_value", "result_units"), sep = " ", convert = TRUE) %>% 
  separate(col = mcl, into = c("mcl_value", "mcl_units"), sep = " ", convert = TRUE)

fips_codes <- read_csv("data/fips-codes.csv") %>% 
  clean_names() %>% 
  mutate(name = tolower(name))
```


```{r}
act_vio_fips <- left_join(act_vio, fips_codes, by = c("county" = "name"))

# Calculate differences for each analyte
# This likely is of little value as health effect for each analyte may be difference
# Ex: small increase in arsenic may be of greater concern than iron
# act_vio_fips %>% 
#   group_by(analyte_name) %>% 
#   summarize(med_above_threshold = median(above_threshold, na.rm = T))
```

```{r}
# all violations by county (all time)
act_vio %>% 
  group_by(county) %>% 
  count() %>% 
  ungroup() %>% 
  right_join(ca_counties, by = c("county" = "county_name")) %>% 
  ggplot(aes(long, lat, group = group, fill = n)) +
    geom_polygon(fill = "grey", color = "#ffffff", size = 0.05) +
    coord_map(projection = "albers", lat0 = 39, lat1 = 45)

# all violations by county (by year)
```